---
title: "Social Survey"
author: "Avelyn Potot"
date: "11/21/2017"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS_2014_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction
<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!--> 

####This study deals with questions about possible relationships between gun ownership and race, sex, political views, opinions on capitol punishment and belief in god. The data is from the 2014 general social survey.
>In this project we are going to show the relationship between gun ownership base on race,sex,political views, opinions on capitol punishment and believe in God.The data is from 2014 general social survey. We will answer all the questions by showing the graph and data as well as the numerical results.
We will base our study on the given packages we have on hand.
>We will study the following hypothesis such as:

First question: Is there a relationship between gun ownership and race? 

$H_0$: there is no relationship between gun ownrship between gun ownership and race.
$H_A$: there is a relationship between gun ownership and race.

Second question: Is there a relationship between gun ownership and sex? 

$H_0$: there is no relationship between gun ownership between gun ownership and sex.
$H_A$: there is a relationship between gun ownership and sex. 

Third question: Is there a relationship between gun ownership and opinion about capitol punishment?

$H_0$: there is no relationship between gun ownership and the opinion about capital punishment..
$H_A$: there is a relationship between gun ownership and opinion about capital punishment.

Fourth question: Is there a relationship between gun ownership and belief in god? 

$H_0$: there is no relationship between gun ownrship between gun ownership and belief in god.
$H_A$: there is a relationship between gun ownership and the beief in god. 

Fifth question: Is there a relationship between gun ownership and belief in god? 

$H_0$: there is no relationship between gun ownrship between gun ownership and political views.
$H_A$: there is a relationship between gun ownership and poitical views.


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
>We will use the givin packages for our methods such as sources,dplyer,variable of interest,makeTables,gss,someplots,graphical method, barchartGC, chisqtestG and such.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results
>Since the data is so large it must be narrowed down by using r code in a .R file. The GSS data displays 3842 observations so we use the dplyr package to extract 12 variables

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

>Gun Ownership vs. capitol punishment
```{r}
source("makeTables.R")
source("someplots.R")
barchartGC(cappun_table,type="percent")
```

After viewing the data graphically, it appears that there are more NO to the favor side than yes, while there  are more NO to the oppose side than yes.

>Gun Ownership vs.God
```{r}
source("makeTables.R")
source("someplots.R")
barchartGC(god_table,type="percent")
```

It looks like that there is a relationship between the gun ownership and God.Those in NO group are highly opposing the gun ownership.Those in MAYBE and YES graph for NO group are also highly opposing the gun ownership as well.For YES group, it appears that it also have the same percentage for no,maybe and yes graph. However, the NO graph has high majority. 

>Gun Ownership vs. Race
```{r}
source("makeTables.R")
source("someplots.R")
barchartGC(race_table,type="percent")
```

It appears that for BLACK and OTHER, more believe in NO gun ownership than YES. For WHITE, more appear in NO group than YES too.

>Gun Ownership vs. Sex
```{r}
source("makeTables.R")
source("someplots.R")
barchartGC(sex_table,type="percent")
```

It appears that between male and female, They both are likely don`t believe in gun ownership.However there are more majority in female in NO group than male base on graphical result.

>Gun ownership vs. Political Views
```{r}
source("makeTables.R")
source("someplots.R")
barchartGC(polviews_table,type="percent")
```
It appears that the Liberal are highly opposing the gun ownership.It has a vast majority of NO group on our graphical data. The Mode
rate and COnservative are likely not believe in gun ownership too. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

>To view the results of our data numerically, we will use a makeTables.R using the rowPerc function from the tigerstats package.

Gun ownership vs.Cappun_table
```{r}
rowPerc(cappun_table)
```

Of those in the FAVOR group,41.44% are in YES in gun ownership, 58.56% in NO. that 
Of those in the OPPOSE group,20.58% are YES in gun ownership,79.42% in NO.
After viewing the data numerically, It appears that between FAVOR and OPPOSE,there are more percentage in NO gun ownership than YES for gun ownership.

>Gun ownership vs. god_table
```{r}
rowPerc(god_table)
```

Of those in NO group,32.46% are YES in gun ownership,67.54% do not.
Of those in MAYBE group,33.33% are YES in gun wonership,66.67% do not.
Of those in YES group,33.05% are YES in gun ownership,66.95% do not.
After viewing the data numerically, It appears that for YES, NO and MAYBE group has a large majority of NO in gun ownership.

>Gun Ownerhip vs. race_table
```{r}
rowPerc(race_table)
```

Of those in the WHITE group,39.01% in YES in gun ownership,60.99% in NO for gun ownership.
Of those in BLACK group,16.87% in YES in gun ownership,83.13% in NO for gun ownership.
Of those in the OTHER group,13.93% in YES in gun ownership,86.07% are NO for gun ownership.
After viewing the data numerically, IT appears that WHITE, BLACK and OTHER has a large majority in NO for gun ownership.

>GUn Ownership vs. sex_table
```{r}
rowPerc(sex_table)
```

Of those in the MALE group,39.76% are YES in gun ownership,60.24% in NO for gun ownership.
Of those in FEMALE group,27.32% are in YES for ownership,72.68% for NO in gun ownership.
After viewing the data numerically,It appears that a high majority of MALE and FEMALE group are both have a high majority of NO for gun ownership.

>Gun Owneship vs.polviews_table
```{r}
rowPerc(polviews_table)
```

Of those in MODERATE group,33.20% are YES in gun wonership,66.80 in NO for gun ownership.
OF those in CONSERVATIVE group,42.17% are YES in gun ownership,57.83% in NO for gun ownership.
After viewing the data numerically,It appears that those in Liberal group are overwhelmingly more likely to oppose in gun ownership and the MODERATE group as well as CONSERVATIVE group are also more likely not favor in gun ownership.

# Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
>We will need to run the test using chisqtestGC function from the tigerstats package.We will run each test to see if what and who is more favor for gun ownership between our varibale such as capitol punishment, god, race, sex and political views.

>Gun Ownership vs.cappun chi-square test:

Let us begin by forming our two hypothesis:

$H_0$: there is no relationship between gun ownership and the opinion about capital punishment.

$H_A$: there is a relationship between gun ownership and opinion about capital punishment.

```{r}
chisqtestGC(cappun_table)
```

Our p-value is 0. This means the probablity of having a result like this data when null hypothesis is true. Since the p-value is too low we will reject the null hypothesis and conclude that there is a relationship between gun ownership and opinion about capital punishment.

>Gun Ownership vs.God chi-square test:

We will form our two hypothesis:

$H_0$: there is no relationship between gun ownrship between gun ownership and belief in god.

$H_A$: there is a relationship between gun ownership and the beief in god. 

```{r}
chisqtestGC(god_table)
```

Our p-value is 0.9739. This means the probability getting a result like this data is under conditions when the null hypothesis is true,is about 1 in 100(about 100%)This is higher a lil bit of NO for gun ownership(which is typically 5 percent mostly).Since p-value is not more than at 1, we will reject the null hypothesis and conclude that there is a relationship between god in gun ownership.

>Gun Ownership vs.Race chi-square test :

We will form our two hypothesis:

$H_0$: there is no relationship between gun ownrship between gun ownership and race.

$H_A$: there is a relationship between gun ownership and race.
```{r}
chisqtestGC(race_table)
```

Our p-value is 0. The chances of getting such a result are small if the hypothesis is true.We therefore choose to reject the null hypothesis.So it appears that gun ownership and race are related.

>GUn Ownership vs.Sex chi-square test:

We will form our two hypothesis:

$H_0$: there is no relationship between gun ownership between gun ownership and sex.

$H_A$: there is a relationship between gun ownership and sex. 

```{r}
chisqtestGC(sex_table)
```

Our p-value is 0. The chances of getting such a result are small if the null hypothesis is true. We therefore choose to reject the null hypothesis. So it appears that sex and gun ownership are related.

>GUn Ownership vs.Political views chi-square test:

We will form our two hypothesis:

$H_0$: there is no relationship between gun ownrship between gun ownership and political views.

$H_A$: there is a relationship between gun ownership and poitical views.
```{r}
chisqtestGC(polviews_table)
```

Our p-value is 0.The chance of getting such a result are so small if the null hypothesis is true. We therefore choose to reject the null hypothesis. So it appears that political views and gun ownership are related, with a higher level of political views leading to greater chance of NO in gun ownership.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

After viewing the results graphically,numerically and running chi-square tests on the data, we can conclude the following:

Capitol punishment and gun ownership are related.The FAVOR and OPPOSE group are more likely to say NO to gun ownership.
God and gun ownership are related. Even though it is in the borderline of to become 1% it is still considered less likely to say YES in gun ownnership. The NO,YES and OTHER are more likely to say NO to gun ownership.
Race and gun ownership are related.The WHITE,BLACK and OTHER group are more likely to say NO to gun ownership.
Sex and gun ownership are related. The MALE and FEMALE are more likely to say NO to gun ownership.
Political views and gun ownership are highly related.The LIBERAL,MODERATE and CONSERVATIVE group are more likely to say NO to gun  ownership.

If we were to make a profile of those who do not believe for having a gun it would be all our variables.So, without taking any variables into account,It appears that there is a relationship between capitol punishment, god, race, sex and political views when it comes to saying NO to gun ownership.With the GSS data of 2014, there are many factors we could compare.
